---
title: "Portfolio 1"
---

> Goal:
For the first portfolio, the goal is to use some of the tools we have learned in earlier modules and more to clean, summarize, and visualize a Gamelytics dataset from Kaggle. I will also try to evaluate whether a new promotional offer(the test group) improves user (player) outcomes compared to the current offer (control group) using A/B tsting foor the conversion rate and revenue per use, as suggested as part of the Kaggle challenges for this dataset. For the purpose of this protfolio, we are going to assume the revenue is in dollars as there is no indication of currency in the description. 



#Will start by loading all the packages I may be using for this. 

```{r load-packages, warning = FALSE, message=FALSE}
library(tidyverse) 
library(tidyr)
library(ggplot2)
```


#Import a/b test data (csv, separated by semicolon; used delim)
```{r import-dataset}
library(readr)
ab_test <- read_delim("C:/Users/psy_user/Downloads/Data science/ab_test.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
View(ab_test)
```

#Do a quick check/poke around the dataset. 

```{r data-quick-check}
names(ab_test)  #checking if the file is read correctly
glimpse(ab_test)
```

Here is some quick guide to what each column is measuring:

user_id: A unique identifier for each user

revenue: The revenue generated by the user

testgroup: The group to which the user was assigned (object, e.g., “a” or “b”)

Quick check into the revenue data we have

```{r revenue-data-check}
summary(ab_test$revenue)
```

It looks like the data is very spread out. Let's visualize this. 

```{r revenue-histogram}
ggplot(ab_test, aes(x = revenue)) + 
  geom_histogram() +
  labs (
    title = "Distribution of Gamelytics Revenue",
    x = "Revenue Generated by User ($)",
    y = "Number of Users"
  ) +
  theme_bw()
```

The data is heavily right-skewed. A lot of people did not pay anything at all, while there is a very small number of people paying about less than $10,000. We have also seen that the maximum amount spent is a little under $40,000. 



Next, I wanted to do a quick check into the test groups.

```{r}
ab_test %>% count(testgroup)
```

Looks like the number of people in the two groups are pretty balanced, and we have a very large sample size for both groups. 

Because there are few people that have spent money, it's not very helpful to visualize if they're mixed together with the majority of the population which are non-payers. So, I am creating a new variable that shows who paid. 

```{r add-payer-variable}
ab <- ab_test %>%
  mutate (payer_user = revenue > 0)
```

```{r quick-check-before-moving-to-other-stuff}
ab %>% count (payer_user)
```

```{r visualize-payer-nonpayer}
ab %>%
  count(payer_user) %>%
  ggplot(aes(x = payer_user, y = n, fill = payer_user)) + 
  geom_col() +
  labs (
    title = "Gamelytics Paying vs Non-Paying Users",
    x = "Is the user paying?",
    y = "Number of Users",
    fill = "User is payer"
  ) +
  theme_bw()
```




