---
title: "Portfolio 1: Gamelytics: Mobile Game Analytics Challenge"
---

> Goal:
For the first portfolio, the goal is to use some of the tools we have learned in earlier modules and more to clean, summarize, and visualize a Gamelytics dataset from Kaggle. I will also try to evaluate whether a new promotional offer(the test group) improves user (player) outcomes compared to the current offer (control group) using A/B testing for the conversion rate and revenue per use, as suggested as part of the Kaggle challenges for this dataset. For the purpose of this protfolio, we are going to assume the revenue is in dollars as there is no indication of currency in the description. 


#Will start by loading all the packages I may be using for this. 

```{r load-packages, warning = FALSE, message=FALSE}
library(tidyverse) 
library(tidyr)
library(ggplot2)
```


#Import a/b test data (csv, separated by semicolon; used delim)
```{r import-dataset}
library(readr)
ab_test <- read_delim("C:/Users/psy_user/Downloads/Data science/ab_test.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
View(ab_test)
```

#Do a quick check/poke around the dataset. 

```{r data-quick-check}
names(ab_test)  #checking if the file is read correctly
glimpse(ab_test)
```

Here is some quick guide to what each column is measuring:

user_id: A unique identifier for each user

revenue: The revenue generated by the user

testgroup: The group to which the user was assigned (object, e.g., “a” or “b”)

Quick check into the revenue data we have

```{r revenue-data-check}
summary(ab_test$revenue)
```

It looks like the data is very spread out. Let's visualize this. 

```{r revenue-histogram}
ggplot(ab_test, aes(x = revenue)) + 
  geom_histogram() +
  labs (
    title = "Distribution of Gamelytics Revenue",
    x = "Revenue Generated by User ($)",
    y = "Number of Users"
  ) +
  theme_bw()
```

The data is heavily right-skewed. A lot of people did not pay anything at all, while there is a very small number of people paying about less than $10,000. We have also seen that the maximum amount spent is a little under $40,000. 



Next, I wanted to do a quick check into the test groups.

```{r}
ab_test %>% count(testgroup)
```

Looks like the number of people in the two groups are pretty balanced, and we have a very large sample size for both groups. 

Because there are only few people that have spent money, it's not very helpful to visualize if they're mixed together with the majority of the population which are non-payers. So, I am creating a new variable that shows who paid. 

```{r add-payer-variable}
ab <- ab_test %>%
  mutate (payer_user = revenue > 0)
```

```{r quick-check-before-moving-to-other-stuff}
ab %>% count (payer_user)
```

```{r visualize-payer-nonpayer}
ab %>%
  count(payer_user) %>%
  ggplot(aes(x = payer_user, y = n, fill = payer_user)) + 
  geom_col() +
  labs (
    title = "Gamelytics: Paying vs Non-Paying Users",
    x = "Is the user paying?",
    y = "Number of Users",
    fill = "User is payer"
  ) +
  theme_bw()
```

### Conversion Rates

Now that I have differentiated who is paying, I would like to take a look at the conversion rate (percent of users who pay) in both groups. 

```{r conversion-rate-by-group}
conv_rate_by_group <- ab %>%
  group_by(testgroup) %>%   #split the data into group a and b
  summarise(
    conversion_rate = mean(payer_user),  #what proportion paid in each group  
    n_users = n(),   #how many users in each group
    .groups = "drop"
  )
```

We can see that there are `r scales::percent(mean(ab$payer_user[ab$testgroup == "a"]), accuracy = 0.01)` of paying users in test group 'a' and `r scales::percent(mean(ab$payer_user[ab$testgroup == "b"]), accuracy = 0.01)` paying users in test group 'b'.

```{r visualize-conversion-rate}
ggplot (conv_rate_by_group,
        aes(x = testgroup,
            y = conversion_rate, 
            fill = testgroup)) + 
  geom_col() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.01)) +
  scale_fill_manual(values = c("a" = "orange",
                               "b" = "steelblue")) +
  labs (
    title = "Conversion Rate by Test Group",
    x = "Test Group",
    y = "Conversion Rate (%)",
    fill = "Group"
  ) +
  theme_bw()

```

Now that we know what percentage of users paid in each group, this doesn't really tell us the full story. We only know that slightly more people paid in group 'a' But we would also want to know how much these paying users are spending. 

### Average Revenue Per User (ARPU)

I will calculate the average revenue spent per user (total revenue in group/total number of users in group).We are now incorporating th conversion rates with their level of spending. 

```{r calculate-ARPU-by-group}
ARPU_by_group <- ab %>% 
  group_by(testgroup) %>%
  summarise(
    ARPU = mean(revenue),   #calculate the mean of revenue now (instead of paying user)
    n_users = n ()
  )
```

```{r visualize_ARPU}
ggplot(ARPU_by_group,
       aes(x = testgroup,
           y = ARPU, 
           fill = testgroup)) + 
  geom_col() + 
  scale_fill_manual(values = c("a" = "firebrick",
                               "b" = "forestgreen")) +
  labs (
    title = "Average Revenue Per User by Test Group",
    x = "Test Group",
    y = "ARPU ($)",
    fill = "Group"
  ) +
  theme_bw()
  
```

This is a bit interesting. Earlier the conversion rate calculation showed us that Group A has slightly more number of users that are paying. But, now we see that in Group B, there is slightly more money spent per user overall. This suggests that although slightly fewer users are making purchases in Group B, those who do may be spending more on average compared to Group A. It's important to note that the outliers may be affecting our data though since our revenue distribution is really skewed. 

### Revenue Distribution by Group

```{r revenue-histogram-by-group}
ggplot(ab, aes(x = revenue, fill = testgroup)) +
  geom_histogram() +
facet_wrap(~testgroup) +
  labs(
    title = "Revenue Distribution by Test Group",
    x = "Revenue ($)",
    y = "Number of Users"
  ) +
  theme_bw() +
  theme(legend.position = "none")
```

